---
title: "&nbsp;"
title-meta: Method Validation-Report
params:
  inp_data: NA
  logo_file: NA
  V_pars: NA
  helptext_v_fig_V1: NA
  helptext_v_tab_V1: NA
  helptext_v_formula_collection : NA
output:
  word_document: default
  html_document:
    df_print: paged
fontsize: 11pt
always_allow_html: true
---

<!-- This is a reminder how the font-size within a DT table can be set globally for the whole document using css -->
<!-- ```{css, eval = TRUE, echo = FALSE} -->
<!-- .dataTables_wrapper { -->
<!--     font-size: 200%; -->
<!-- } -->
<!-- ``` -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(out.width = '100%', dpi=300)
if (!knitr::is_html_output()) library(webshot2)
fs_tab <- "175%"
prec <- params$V_pars$opt_tabV1_precision
ab <- eCerto:::prepDataV1(tab=params$inp_data, a = params$V_pars$opt_figV1_anal, l = params$V_pars$opt_figV1_level, fmt = "rel_norm")
fig_V1_width <- eCerto:::calc_bxp_width(n = length(params$V_pars$opt_figV1_anal)*length(params$V_pars$opt_figV1_level), w_point = 28, w_axes = 120)
tab_v1 <- eCerto:::prepTabV1(
  tab = eCerto:::flt_Vdata(
    x = params$inp_data, 
    l = if (params$V_pars$opt_tabV1_useLevels) params$V_pars$opt_figV1_level else NULL, 
    a = if (params$V_pars$opt_tabV1_useAnalytes) params$V_pars$opt_figV1_anal else NULL
  ),
  alpha = params$V_pars$opt_tabV1_alpha,
  k = params$V_pars$opt_tabV1_k,
  flt_outliers = params$V_pars$opt_tabV1_fltLevels,
  unit_cali = params$V_pars$opt_tabV1_unitcali,
  unit_smpl = params$V_pars$opt_tabV1_unitsmpl,
  conv_fac = params$V_pars$opt_tabV1_convfac
)
```


<!-- In HTML the logo is right aligned. Unfortunately the option fig.align is not supported in Word -->
```{r Logo, echo=FALSE, out.width="20%", fig.align="right"}
  knitr::include_graphics(params$logo_file)
```

# ***eCerto*** Report

**Date: `r format(Sys.time(), '%d %B, %Y')`**

## Modul: Method validation

```{r helptext_v_fig_V1, results='asis'}
  cat(params$helptext_v_fig_V1, sep = "\n")
```

```{r fig_V1, echo=FALSE, fig.width=fig_V1_width/96, fig.dpi=96, fig.retina=4}
  eCerto:::prepFigV1(ab = ab)
```

The working range concentrations within the solutions and samples, respectively, 
are provided in the following table.

```{r tab_V1_wr, message=FALSE, resize.width="100%"}
tab_V1_wr <- eCerto:::style_tabV1(df = tab_v1, precision = prec, selected = NULL, interact_ele = FALSE, show_colgroups = "wr")
if (knitr::is_html_output()) {
  tab_V1_wr
} else {
  colnames(tab_V1_wr$x$data) <- eCerto:::HTML2markdown(colnames(tab_V1_wr$x$data))
  knitr::kable(tab_V1_wr$x$data, digits = prec)
}
```

```{r tab_V1_wr_word, echo=FALSE, message=FALSE, fig.width=1440/96, fig.dpi=96, fig.retina=4}
if (!knitr::is_html_output()) eCerto:::style_tabV1(df = tab_v1, precision = prec, selected = NULL, interact_ele = FALSE, font.size = fs_tab, show_colgroups = "wr")
```

In the following, detailed plots for the levels determining the working range for
each analyte are presented.

```{r fig_V1_details, echo=FALSE, fig.height=880/96, fig.width=640/96}
  inp <- params$inp_data
  tab <- tab_v1
  as <- tab$Analyte
  for (a in as) {
    L_min <- tab[tab$Analyte==a,"c_WR_min"]
    L_max <- tab[tab$Analyte==a,"c_WR_max"]
    Ls <- sapply(c(L_min, L_max), function(x) {
      unique(inp[inp[,"Analyte"]==a & abs(inp[,"Concentration"]-as.numeric(x))<0.001,"Level"])[1]
    })
    flt <- inp[,"Analyte"] %in% a & inp[,"Level"] %in% Ls
    eCerto:::prepFigV3(x = inp[flt,,drop=FALSE], cex = 1)
  }
```

<!-- Yihui suggested the \newpage command here https://bookdown.org/yihui/rmarkdown-cookbook/pagebreaks.html to achieve a page break -->
<!-- In theory the div approach should work as well but doesn't in this report when converted to Word -->
<!-- <div style="page-break-after: always;"></div> -->
\newpage

```{r helptext_v_tab_V1, results='asis'}
  cat(params$helptext_v_tab_V1, sep = "\n")
```

Linear model parameters for all analytes are provided in the following table.

```{r tab_V1_lm, message=FALSE, resize.width="100%"}
tab_V1_lm <- eCerto:::style_tabV1(df = tab_v1, precision = prec, selected = NULL, interact_ele = FALSE, show_colgroups = "lm")
if (knitr::is_html_output()) {
  tab_V1_lm
} else {
  colnames(tab_V1_lm$x$data) <- eCerto:::HTML2markdown(colnames(tab_V1_lm$x$data))
  knitr::kable(tab_V1_lm$x$data, digits = prec, caption = tab_V1_lm$x$caption)
}
```

```{r tab_V1_lm_word, echo=FALSE, message=FALSE, fig.width=1440/96, fig.dpi=96, fig.retina=4}
if (!knitr::is_html_output()) eCerto:::style_tabV1(df = tab_v1, precision = prec, selected = NULL, interact_ele = FALSE, font.size = fs_tab, show_colgroups = "lm")
```

In the following, detailed plots comparing linear and quadratic model fits for
each analyte are presented.

```{r tab_V1_details, echo=FALSE, message=FALSE, fig.height=880/96, fig.width=640/96}
  inp <- params$inp_data
  tab <- tab_v1
  flt_outliers <- length(grep("^[(]", tab[,"F_Test"]))>=1
  as <- tab$Analyte
  for (a in as) {
    L_min <- tab[tab$Analyte==a,"c_WR_min"]
    L_max <- tab[tab$Analyte==a,"c_WR_max"]
    Ls <- sapply(c(L_min, L_max), function(x) {
      unique(inp[inp[,"Analyte"]==a & abs(inp[,"Concentration"]-as.numeric(x))<0.001,"Level"])[1]
    })
    idx <- as.numeric(levels(inp[,"Level"])[which(levels(inp[,"Level"]) %in% Ls)])
    Ls <- levels(inp[,"Level"])[idx[1]:idx[2]]
    flt <- inp[,"Analyte"] %in% a & inp[,"Level"] %in% Ls
    eCerto:::prepFigV2(tab = inp[flt,,drop=FALSE], a = a, flt_outliers = flt_outliers, cex = 1)
  }
```

\newpage

### Limit of Detection and Quantification

Based on the linear models specified above the following LOD and LOQ values were 
determined for all analytes.

```{r tab_V1_lox, message=FALSE, resize.width="100%"}
  tab_V1_lox <- eCerto:::style_tabV1(df = tab_v1, precision = prec, selected = NULL, interact_ele = FALSE, show_colgroups = "lo")
  if (knitr::is_html_output()) {
    tab_V1_lox
  } else {
    knitr::kable(tab_V1_lox$x$data, digits = prec)
  }
```

```{r tab_V1_lox_word, echo=FALSE, message=FALSE, fig.width=1440/96, fig.dpi=96, fig.retina=4}
if (!knitr::is_html_output()) eCerto:::style_tabV1(df = tab_v1, precision = prec, selected = NULL, interact_ele = FALSE, font.size = fs_tab, show_colgroups = "lo")
```

\newpage

### Trueness

```{r txt_trueness, results='asis'}
  cat(params$V_pars$txt_trueness, sep = "\n")
```

\newpage

### Precision

```{r txt_precision, results='asis'}
  cat(params$V_pars$txt_precision, sep = "\n")
```

\newpage

### Measurement Uncertainty

```{r txt_uncertainty, results='asis'}
  cat(params$V_pars$txt_uncertainty, sep = "\n")
```

\newpage

```{r helptext_v_formula_collection, results='asis'}
  cat(params$helptext_v_formula_collection, sep = "\n")
```

\newpage

### Input data for reference

Finally, this is the input data table as used internally for all calculations.

```{r inp_tab, echo=FALSE, resize.width="100%"}
inp <- params$inp_data
inp <- inp[inp[,"Analyte"] %in% tab_v1$Analyte,]
inp <- inp[, !(colnames(inp) %in% c("Type", "Exclude_Level", "Exclude_Sample", "norm", "rel_norm"))]
if (knitr::is_html_output()) {
  DT::datatable(
    data = inp, rownames = FALSE, extensions = "Buttons", 
    options = list(dom = "Bt", pageLength = -1, buttons = list(list(extend = "excel", text = "Excel", title = NULL)))
  )
} else {
  knitr::kable(inp, row.names = FALSE, digits = prec+1)
}
```
