---
title-meta: "LTS-Report"
output:
  pdf_document: 
    latex_engine: lualatex
  html_document:
    df_print: paged
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{fontspec}
- "\\setmainfont{BAMKlavika-Light.ttf}[BoldFont = BAMKlavika-Medium.ttf, ItalicFont
  = BAMKlavika-LightItalic.ttf, BoldItalicFont = BAMKlavika-MediumItalic.ttf]"
params:
  dat: NA
  logo_file: NA
  fnc: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# the number of lines for the table fitting on a page
l_max <- 45
# the index of the KW which the report is generated for (currently fixed to 1)
i <- 1

# is the Rmd processing in testing mode (not called by the Shiny App)
testing <- length(params$dat)==1L && (is.na(params$dat) | params$dat=="NA")
if (testing) {
  report_file <- system.file("app/www/reports/report_vorlage_lts.Rmd", package = "eCerto")
  load(file = system.file("app/www/LTS001.RData", package = "eCerto"))
  d <- LTS_dat[[i]][["def"]]
  v <- LTS_dat[[i]][["val"]]
  l <- "BAMLogo2015.png"
  if (!file.exists(file.path(dirname(report_file), l))) {
    warning(l, " is not in same folder as ", basename(report_file))
  }
  plot_lts_data <- eCerto::plot_lts_data
} else {
  d <- params[["dat"]][[i]][["def"]]
  v <- params[["dat"]][[i]][["val"]]
  l <- params[["logo_file"]]
  plot_lts_data <- params[["fnc"]][["plot_lts_data"]]
}
```

```{r logo, echo=FALSE, fig.align='right', fig.height = 0.5}
# show BAM Logo topright
if (!(is.null(l) | is.na(l))) {
    logo_raster <- as.raster(magick::image_read(path = l))
    par(mar=c(1,0,0,0))
    layout(mat = matrix(1:2,ncol = 2), widths = c(0.8,0.2))
    plot(1,1,axes=F,ann=F, type="n")
    mtext(side = 3, line = -1, text = "Long-Term Stability (LTS)", adj = 0, font=2)
    mtext(side = 3, line = -2.25, text = paste("Material:", d[,"RM"]), adj = 0)
    mtext(side = 3, line = -2.25, text = paste("Date:", format(Sys.time(), '%Y-%m-%d')), adj = 0.75)
    plot(logo_raster)
}
  
```

```{r plots, echo=FALSE, results='asis', dev.args = list(pointsize = 9), fig.height = 3.5}
  # 2 plots as in App version
  par(mar=c(5,4,4,2)+0.1)
  par(mfrow=c(1,2))
    x <- list("val"=v, "def"=d)
    plot_lts_data(x = x, type=1)
    lts <- plot_lts_data(x = x, type=2)
  par(mfrow=c(1,1))
```

```{r stats}
U_lts_rel <- sd(v[,"Value"])/median(v[,"Value"])
s_x <- sd(v[,"Value"])/sqrt(nrow(v))
s_xrel <- s_x/median(v[,"Value"])
CI <- sd(v[,"Value"])*qt(0.975, nrow(v)-1)/sqrt(nrow(v)-1)
U_ilc <- round(100*d[,"U"]/d[,"CertVal"],2)
U_lts <- round(100*switch(d[,"U_Def"], "1s"=U_lts_rel, "2s"=2*U_lts_rel, "CI"=CI/median(v[,"Value"]), "1sx"=s_xrel, "2sx"=2*s_xrel), 2)
n_digits <- nchar(strsplit(as.character(d[,"CertVal"]), "[.]")[[1]][2])
tab1_property_string <- paste0(d[,"KW_Def"], " (", d[,"KW"],")")
tab1_cert_val_string <- paste(d[,"CertVal"], "±",  d[,"U"], "/", 100*d[,"Coef_of_Var"], "rel. [%] (", d[,"U_Def"], ")", d[,"KW_Unit"])
tab2_median_val_string <- paste(round(median(v[,"Value"]), n_digits), d[,"KW_Unit"])
```

**RM Informations**

|      |           |
| ---: | :-------- |
| Name:                        | **`r d[,"RM"]`**             |
| Property:                    | **`r tab1_property_string`** |
| Certified Value:             | **`r tab1_cert_val_string`** |
| Number of accepted datasets: | **`r d[,"acc_Datasets"]`**   |

**Statistical Information monitoring (LTS)**

|        |     |     |     |     |
| -----: | --- | --- | --- | --- |
| Number of measurements:                          | **`r nrow(v)`**                      |                                        | Median:                                | **`r tab2_median_val_string`**                |
| Standarddeviation:                               | **s=`r round(sd(v[,"Value"]), 2)`**  | **s~rel~=`r round(100*U_lts_rel,2)`%** | **2s=`r round(2*sd(v[,"Value"]), 2)`** | **2s~rel~=`r round(2*100*U_lts_rel,2)`%**     |
| Standarddeviation of mean:                       | **s~x~=`r round(s_x, 4)`**           | **s~x,rel~=`r round(100*s_xrel,2)`%**  | **2s~x~=`r round(2*s_x, 4)`**          | **2s~x,rel~=`r round(2*100*s_xrel,2)`%**      |
| Confidence interval:                             | (CI~0.95~)                           | **`r round(CI, 4)`**                   | (CI~0.95,rel~)                         | **`r round(100*CI/median(v[,"Value"]), 2)`%** |

**Results**

The uncertainty **`r d[,"U_Def"]`~rel~=`r U_ilc`%** determined from an interlaboratory comparison (ILC) is \textcolor{`r ifelse(U_ilc > U_lts, "green", "red")`}{`r ifelse(U_ilc > U_lts, "larger", "smaller")`} than the uncertainty value **`r d[,"U_Def"]`~rel~=`r U_lts`%** determined within the LTS monitoring.

The long-term stability for the reference material **`r d[,"RM"]`** with its property of **`r d[,"KW_Def"]`** was determined as \textcolor{`r ifelse(lts > 60, "green", "red")`}{`r lts`} month (`r names(lts)`).

\textcolor{gray}{All measurement data and potential comments are enlisted on the following page.}

\pagebreak

```{r datatable, echo=FALSE, results='asis'}
  #cat("\n\n\\pagebreak\n")
  # table of values (potentially modified)
  com <- v[,"Comment"]
  out <- v[,1:3]
  if (any(!is.na(com))) {
    out$C <- ""
    out$C[!is.na(com)] <- 1:sum(!is.na(com))
    com <- com[!is.na(com)]
  } else {
    com <- NULL
  }
  if (nrow(out)>l_max & nrow(out)<2*l_max) {
    n_fill <- 2*l_max-nrow(out)
    dummy <- data.frame(out[1:n_fill,])
    for (j in 1:ncol(dummy)) dummy[,j] <- rep(NA,n_fill)
    out <- cbind(out[1:l_max,], rbind(out[(l_max+1):nrow(out),], dummy))
  }
  opts <- options(knitr.kable.NA = "")
  #print(knitr::kable(x=data.frame("X"=1:3,"Y"=LETTERS[1:3]), format="latex", row.names = FALSE))
  kableExtra::footnote(
    kableExtra::kable_styling(
      kable_input = knitr::kable(x=out, format="latex", row.names = FALSE),
      latex_options = "striped", font_size = 8
    ),
  number=com)
```
