---
title: "&nbsp;"
title-meta: Method Validation-Report
params:
  inp_data: NA
  tab_V1: NA
  fig_V1: NA
  fig_V1_width: NA
  logo_file: NA
  V_pars: NA
  helptext_v_fig_V1: NA
  helptext_v_tab_V1: NA
  helptext_v_formula_collection : NA
output:
  word_document: default
  html_document:
    df_print: paged
fontsize: 11pt
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(out.width = '100%', dpi=300)
if (!knitr::is_html_output()) library(webshot2)
```

```{r Logo, echo=FALSE, out.width="20%", fig.align="right"}
  knitr::include_graphics(params$logo_file)
```

# ***eCerto*** Report

**Date: `r format(Sys.time(), '%d %B, %Y')`**

## Modul: Method validation

```{r helptext_v_fig_V1, results='asis'}
  cat(params$helptext_v_fig_V1, sep = "\n")
```

```{r fig_V1, echo=FALSE, fig.width=params$fig_V1_width/96, fig.dpi=96, fig.retina=4}
  params$fig_V1()
```

In the following, detailed plots for the levels determining the working range for
each analyte are presented.

```{r fig_V1_details, echo=FALSE, fig.height=780/96}
  inp <- params$inp_data
  tab <- params$tab_V1
  as <- tab$Analyte
  for (a in as) {
    L_min <- tab[tab$Analyte==a,"c_WR_min"]
    L_max <- tab[tab$Analyte==a,"c_WR_max"]
    Ls <- sapply(c(L_min, L_max), function(x) {
      unique(inp[inp[,"Analyte"]==a & abs(inp[,"Concentration"]-as.numeric(x))<0.001,"Level"])[1]
    })
    flt <- inp[,"Analyte"] %in% a & inp[,"Level"] %in% Ls
    eCerto:::prepFigV3(x = inp[flt,,drop=FALSE], cex = 1)
  }
```

The working range concentrations within the solutions and samples, respectively, 
are provided in the following table.

```{r tab_V1_wr, message=FALSE, resize.width="100%"}
  if (knitr::is_html_output()) {
    eCerto:::style_tabV1(df = params$tab_V1, precision = params$V_pars$opt_tabV1_precision, selected = NULL, ordering = FALSE, font.size = "90%", show_colgroups = "wr")
  }
```

```{r tab_V1_wr_word, echo=FALSE, message=FALSE, fig.width=1440/96, fig.dpi=96, fig.retina=4}
if (!knitr::is_html_output()) eCerto:::style_tabV1(df = params$tab_V1, precision = params$V_pars$opt_tabV1_precision, selected = NULL, ordering = FALSE, font.size = "120%", show_colgroups = "wr")
```

```{r helptext_v_tab_V1, results='asis'}
  cat(params$helptext_v_tab_V1, sep = "\n")
```

Linear model parameters for all analytes are provided in the following table.

```{r tab_V1_lm, message=FALSE, resize.width="100%"}
  if (knitr::is_html_output()) {
    eCerto:::style_tabV1(df = params$tab_V1, precision = params$V_pars$opt_tabV1_precision, selected = NULL, ordering = FALSE, font.size = "90%", show_colgroups = "lm")
  }
```

```{r tab_V1_lm_word, echo=FALSE, message=FALSE, fig.width=1440/96, fig.dpi=96, fig.retina=4}
if (!knitr::is_html_output()) eCerto:::style_tabV1(df = params$tab_V1, precision = params$V_pars$opt_tabV1_precision, selected = NULL, ordering = FALSE, font.size = "120%", show_colgroups = "lm")
```

In the following, detailed plots comparing linear and quadratic model fits for
each analyte are presented.

```{r tab_V1_details, echo=FALSE, message=FALSE, fig.height=960/96}
  inp <- params$inp_data
  tab <- params$tab_V1
  flt_outliers <- length(grep("^[(]", tab[,"F_Test"]))>=1
  as <- tab$Analyte
  for (a in as) {
    L_min <- tab[tab$Analyte==a,"c_WR_min"]
    L_max <- tab[tab$Analyte==a,"c_WR_max"]
    Ls <- sapply(c(L_min, L_max), function(x) {
      unique(inp[inp[,"Analyte"]==a & abs(inp[,"Concentration"]-as.numeric(x))<0.001,"Level"])[1]
    })
    idx <- as.numeric(levels(inp[,"Level"])[which(levels(inp[,"Level"]) %in% Ls)])
    Ls <- levels(inp[,"Level"])[idx[1]:idx[2]]
    flt <- inp[,"Analyte"] %in% a & inp[,"Level"] %in% Ls
    eCerto:::prepFigV2(tab = inp[flt,,drop=FALSE], a = a, flt_outliers = flt_outliers, cex = 1)
  }
```

### Limit of Detection and Quantification

Based on the linear models specified above the following LOD and LOQ values were 
determined for all analytes.

```{r tab_V1_lox, message=FALSE, resize.width="100%"}
  if (knitr::is_html_output()) {
    eCerto:::style_tabV1(df = params$tab_V1, precision = params$V_pars$opt_tabV1_precision, selected = NULL, ordering = FALSE, font.size = "90%", show_colgroups = "lo")
  }
```

```{r tab_V1_lox_word, echo=FALSE, message=FALSE, fig.width=1440/96, fig.dpi=96, fig.retina=4}
if (!knitr::is_html_output()) eCerto:::style_tabV1(df = params$tab_V1, precision = params$V_pars$opt_tabV1_precision, selected = NULL, ordering = FALSE, font.size = "120%", show_colgroups = "lo")
```

```{r helptext_v_formula_collection, results='asis'}
  cat(params$helptext_v_formula_collection, sep = "\n")
```

### Trueness

```{r txt_trueness, results='asis'}
  cat(params$V_pars$txt_trueness, sep = "\n")
```

### Precision

```{r txt_precision, results='asis'}
  cat(params$V_pars$txt_precision, sep = "\n")
```

### Measurement Uncertainty

```{r txt_trueness, results='asis'}
  cat(params$V_pars$txt_trueness, sep = "\n")
```

### Input data for reference

Finally, this is the input data table as used internally for all calculations.

```{r inp_tab, echo=FALSE, resize.width="100%"}
  inp <- params$inp_data
  tab <- params$tab_V1
  as <- tab$Analyte
  inp <- inp[inp[,"Analyte"] %in% as,]
  if (knitr::is_html_output()) {
    DT::datatable(data = inp, rownames = FALSE, extensions = "Buttons", options = list(dom = "Bt", pageLength = -1, buttons = list(list(extend = "excel", text = "Excel", title = NULL))))
  } else {
    knitr::kable(inp)
  }
```
