---
title: "&nbsp;"
title-meta: Method Validation-Report
params:
  inp_data: NA
  tab_V1: NA
  fig_V1: NA
  fig_V1_width: NA
  logo_file: NA
output:
  html_document:
    df_print: paged
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Logo, echo=FALSE, out.width="20%", fig.align="right"}
  knitr::include_graphics(params$logo_file)
```

## ***eCerto*** Report

**Date: `r format(Sys.time(), '%d %B, %Y')`**

### Modul: Method validation

#### Fig.V1 - Working range

The working range of an analytical method is tested using the relative 
analyte values $x_r$ of the smallest and the largest calibration level, $j_1$
and $j_N$.

Relative analyte values are computed as $x_r = \frac {x_{i,j}} {\overline{x}_j}$ 
with $x_{i,j}$ being the peak area ratios of analyte and internal standard 
$x_{i,j}=\frac{A_\text{Analyte}}{A_\text{IS}}$ for each replicate $i$ at calibration level
$j$.

For each $x_j$ in total $n$ replicate values exist and are tested:

- to follow a normal distribution (Kolmogorof-Smirnov Test, $P_{KS}$)
- to exhibit outliers (Grubbs-Test for single $P_{Grubbs1}$ and double $P_{Grubbs2}$ outliers)
- to show a trend, *i.e.* a drift associated with measurement order (Neumann-Test, $P_{Neumann}$)

The two calibration levels $j_1$ and $j_N$ are tested for homogeneity 
of variance using an F-Test.

```{r fig_V1, echo=FALSE, fig.width=params$fig_V1_width/96, fig.dpi=96, fig.retina=4}
  params$fig_V1()
```

In the following detailed plots for the levels determining the working range for
each analyte are presented.

```{r fig_V1_details, echo=FALSE, fig.height=780/96}
  inp <- params$inp_data$x$data
  tab <- params$tab_V1$x$data
  as <- tab$Analyte
  for (a in as) {
    L_min <- tab[tab$Analyte==a,"c<sub>WR,<i>min</i></sub>"]
    L_max <- tab[tab$Analyte==a,"c<sub>WR,<i>max</i></sub>"]
    Ls <- sapply(c(L_min, L_max), function(x) {
      unique(inp[inp[,"Analyte"]==a & abs(inp[,"Concentration"]-as.numeric(x))<0.001,"Level"])[1]
    })
    flt <- inp[,"Analyte"] %in% a & inp[,"Level"] %in% Ls
    eCerto:::prepFigV3(x = inp[flt,,drop=FALSE], cex = 1)
  }
  
```

#### Tab.V1 - method linearity

The linearity of an analytical method is tested using the analyte values 
$\overline{x}_j$.

Analyte values are computed as the peak area ratios of analyte and internal 
standard $x_{i,j}=\frac{A_{Analyte}}{A_{IS}}$ for each replicate $i$ at 
calibration level $j$. $\overline{x}_j$ is the mean of the $n$ replicates at
level $j$. The total number of calibration levels is denoted as $N$.

For each analyte, a linear model $y=b_0+b_1 \times x$ over all $\overline{x}_j$ 
is computed and the following parameters are reported:

- the number of calibration levels used in the linear model $N$ 
- the smallest number of replicates within all calibration levels $n$
- the probability of error (alpha) selected by the user
- the result uncertainty $k$ selected by the user and depicted as $1/k$ 
- the coefficients $b_0$ (intercept) and $b_1$ (slope) of the linear model
- the limit of detection $\text{LOD}$
- the limit of quantification $\text{LOQ}$
- the standard error of estimate $s_{y,x}$
- the standard error of procedure $s_{x0}$
- the ... $V_{x0}$

Additionally, the residuals $e$ of the linear model are tested:

- to follow a normal distribution (Kolmogorof-Smirnov Test, $P_{KS,Res}$)
- to show a trend, i.e. a drift associated with measurement order (Neumann-Test, $P_{Neu,Res}$)
- for the level showing the highest absolute residual to be an outlier (F-Test, $Out_F$)

For comparison the data is fitted using a quadratic model 
$y=b_0+b_1 \times x+b_2 \times x^2$. The residuals from both models, the linear 
and the quadratic one, are compared using a Mandel-Test calculating $P_{Mandel}$.

```{r tab_V1, resize.width="100%"}
  params$tab_V1
```

In the following detailed plots comparing linear and quadratic model fits for
each analyte are presented.

```{r tab_V1_details, echo=FALSE, fig.height=960/96}
  inp <- params$inp_data$x$data
  tab <- params$tab_V1$x$data
  flt_outliers <- length(grep("^[(]", tab[,"Out<sub>F</sub>"]))>=1
  as <- tab$Analyte
  for (a in as) {
    L_min <- tab[tab$Analyte==a,"c<sub>WR,<i>min</i></sub>"]
    L_max <- tab[tab$Analyte==a,"c<sub>WR,<i>max</i></sub>"]
    Ls <- sapply(c(L_min, L_max), function(x) {
      unique(inp[inp[,"Analyte"]==a & abs(inp[,"Concentration"]-as.numeric(x))<0.001,"Level"])[1]
    })
    idx <- as.numeric(levels(inp[,"Level"])[which(levels(inp[,"Level"]) %in% Ls)])
    Ls <- levels(inp[,"Level"])[idx[1]:idx[2]]
    flt <- inp[,"Analyte"] %in% a & inp[,"Level"] %in% Ls
    eCerto:::prepFigV2(tab = inp[flt,,drop=FALSE], a = a, flt_outliers = flt_outliers, cex = 1)
  }
```

#### Symbol and formula collection

$N_j$ total number of calibration levels with $j$ denoting the j-th level

$n_i$ (minimal) number of replicates within a calibration level with $i$ denoting the i-th replicate

$x_{i,j}$ denoting the peak area ratio of analyte and internal standard (IS) in replicate $i$ of level $j$ calculated as $x_{i,j}=\frac{A_\text {Analyte}}{A_\text {IS}}$ 

$x_r$ denoting the relative analyte level $x_r = \frac {x_{i,j}} {\overline{x}_j}$

$b_0, b_1, (b_2)$ denoting the coefficients (intercept, slope, ...) of a linear (quadratic) model fitting the data

$e$ denoting the residuals (error) of a model

$k$ denoting the result uncertainty specified by the user

$t_{f,\alpha}$ denoting the $t$ distribution with $f$ degrees of freedom and probability $\alpha$

$s_{x,y}$ denoting the standard error of estimate of a linear model of $N$ levels with residuals $e$ calculated as  $s_{x,y}=\sqrt{\frac{\sum e^2}{N-2}}$

$\text {LOD}$ limit of detection of a linear model of $N$ levels with $n$ replicates having slope $b_1$ and residuals $e$ calculated as
$\text {LOD} = k \times \frac {s_{x,y}} {b_1} \times t_{f,\alpha} \times \sqrt {{1 \over n} + {1 \over N} + \frac {\overline{x}^2} {\sum (x-\overline{x})^2}}$
where $f = N-2$ and $\alpha$ is specified by the user

#### Input data for reference

This is the input data table as used internally for all calculations.

```{r inp_tab, echo=FALSE}
  params$inp_data
```

