---
output: 
  pdf_document:
    latex_engine: lualatex
# fontfamily: merriweather
# fontfamilyoptions: sfdefault
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
# - \usepackage[utf8]{inputenc}
- \usepackage{fontspec}
- \setmainfont{BAMKlavika-Light.ttf}[BoldFont = BAMKlavika-Medium.ttf, ItalicFont = BAMKlavika-LightItalic.ttf, BoldItalicFont = BAMKlavika-MediumItalic.ttf]
params:
  dat: NA
  logo_file: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
l_max <- 45
i <- 1
d <- params[["dat"]][[i]][["def"]]
v <- params[["dat"]][[i]][["val"]]
l <- params$logo_file
```

```{r logo, echo=FALSE, fig.align='right', fig.height = 0.5}
# show BAM Logo topright
if (!(is.null(l) | is.na(l))) {
    logo_raster <- as.raster(magick::image_read_svg(path = l, width = 300))
    par(mar=c(0,0,0,0))
    layout(mat = matrix(1:2,ncol = 2), widths = c(0.8,0.2))
    plot(1,1,axes=F,ann=F, type="n")
    mtext(side = 3, line = -1, text = "Long-Term Stability (LTS)", adj = 0, font=2)
    mtext(side = 3, line = -2.25, text = paste("Material:", d[,"RM"]), adj = 0)
    mtext(side = 3, line = -2.25, text = paste("Date:", format(Sys.time(), '%Y-%m-%d')), adj = 0.75)
    plot(logo_raster)
}
  
```

```{r plots, echo=FALSE, results='asis', dev.args = list(pointsize = 9), fig.height = 3.5}
  # 2 plots as in App version
  par(mar=c(5,4,4,2)+0.1)
  par(mfrow=c(1,2))
    plot_lts_data(x = params$dat[[i]], type=1)
    lts <- plot_lts_data(x = params$dat[[i]], type=2)
  par(mfrow=c(1,1))
```

```{r stats}
U_lts_rel <- sd(v[,"Value"])/median(v[,"Value"])
s_x <- sd(v[,"Value"])/sqrt(nrow(v))
s_xrel <- s_x/median(v[,"Value"])
CI <- sd(v[,"Value"])*qt(0.975, nrow(v)-1)/sqrt(nrow(v)-1)
U_ilc <- round(100*d[,"U"]/d[,"CertVal"],2)
U_lts <- round(100*switch(d[,"U_Def"], "1s"=U_lts_rel, "2s"=2*U_lts_rel, "CI"=CI/median(v[,"Value"]), "1sx"=s_xrel, "2sx"=2*s_xrel), 2)
```

**RM Informations**

|                              |                                                                                                         |
|------------------------------|---------------------------------------------------------------------------------------------------------|
| Name:                        | **`r d[,"RM"]`**                                                                                        |
| Property:                    | **`r paste0(d[,"KW_Def"], " (", d[,"KW"],")")`**                                                        |
| Certified Value:             | **`r paste(d[,"CertVal"], "±",  d[,"U"], "/", 100*d[,"Coef_of_Var"], "rel. [%] (1s)", d[,"KW_Unit"])`** |
| Number of accepted datasets: | **`r d[,"acc_Datasets"]`**                                                                              |

**Statistical Information monitoring (LTS)**

|                            |                                                             |                                        |                                        |                                                             |
|----------------------------|-------------------------------------------------------------|----------------------------------------|----------------------------------------|-------------------------------------------------------------|
| Number of measurements:    | **`r nrow(v)`**                                             |                                        | Median:                                | **`r paste(round(median(v[,"Value"]), 2), d[,"KW_Unit"])`** |
| Standarddeviation:         | **s=`r round(sd(v[,"Value"]), 2)`**                         | **s~rel~=`r round(100*U_lts_rel,2)`%** | **2s=`r round(2*sd(v[,"Value"]), 2)`** | **2s~rel~=`r round(2*100*U_lts_rel,2)`%**                   |
| Standarddeviation of mean: | **s~x~=`r round(s_x, 4)`**                                  | **s~x,rel~=`r round(100*s_xrel,2)`%**  | **2s~x~=`r round(2*s_x, 4)`**          | **2s~x,rel~=`r round(2*100*s_xrel,2)`%**                    |
| Confidence interval:       | CI~0.95~                                                    | **`r round(CI, 4)`**                   | CI~0.95,rel~                           | **`r round(100*CI/median(v[,"Value"]), 2)`%**               |

**Results**

The uncertainty **`r d[,"U_Def"]`~rel~=`r U_ilc`%** determined from an interlaboratory comparison (ILC) is \textcolor{`r ifelse(U_ilc > U_lts, "green", "red")`}{`r ifelse(U_ilc > U_lts, "larger", "smaller")`} than the uncertainty value **`r d[,"U_Def"]`~rel~=`r U_lts`%** determined within the LTS monitoring.

The long-term stability for the reference material **`r d[,"RM"]`** with its property of **`r d[,"KW_Def"]`** was determined as \textcolor{`r ifelse(lts > 60, "green", "red")`}{`r lts`} month (`r names(lts)`).

\textcolor{gray}{All measurement data and potential comments are enlisted on the following page.}

```{r datatable, echo=FALSE, results='asis'}
  cat("\n\n\\pagebreak\n")
  # table of values (potentially modified)
  com <- v[,"Comment"]
  out <- v[,1:3]
  if (any(!is.na(com))) {
    out$C <- ""
    out$C[!is.na(com)] <- 1:sum(!is.na(com))
    com <- com[!is.na(com)]
  } else {
    com <- NULL
  }
  if (nrow(out)>l_max & nrow(out)<2*l_max) {
    n_fill <- 2*l_max-nrow(out)
    dummy <- data.frame(out[1:n_fill,])
    for (j in 1:ncol(dummy)) dummy[,j] <- rep(NA,n_fill)
    out <- cbind(out[1:l_max,], rbind(out[(l_max+1):nrow(out),], dummy))
  }
  print(knitr::kable(x=out, row.names = FALSE) %>% kableExtra::kable_styling(latex_options = "striped", font_size = 8) %>% kableExtra::footnote(number=com))
```
