---
title: "Report Vorlage"
output: pdf_document
params:
  General: 'NULL'
  Certification: 'NULL'
  selected_tab: 'NULL'
---
## BAM Tool Report

**Study ID: `r params$General$study_id`**

**Analyte: `r params$selected_tab`**

**User: `r params$General$user`**

**Date: `r format(Sys.time(), '%d %B, %Y')`**

*Testoutput // Designphase*

### Modul: Certification

```{r data, echo=FALSE}
# get a local representation of all data provided by Shiny", 
Zertifizierung <- params$Certification
data <- Zertifizierung$data 
# precision <- Zertifizierung$precision
```

These files have been provided to the tool by `r params$General$user`:

```{r data_files, echo=FALSE, comment=NA}
cat(paste(Zertifizierung$input_files, collapse=",\n"))
```

`r ifelse(any(!Zertifizierung$opt$flt_samples==""), "The following samples (IDs) have been removed by the user:", "")`

```{r, eval=any(!Zertifizierung$opt$flt_samples==\"\"), echo=FALSE, comment=NA} 
cat(paste(Zertifizierung$opt$flt_samples, collapse=", ")) 
```

This is the imported data which was basis for all further calculations:

...