---
params:
  General: NA
  Certification: NA
  Certification_processing: NA
  selected_tab: NA
  logo_file: NA
output:
  html_document:
    df_print: paged
  word_document: 
    reference_docx: template.docx
  pdf_document:
    latex_engine: lualatex
fontsize: 11pt
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE)
  testing <- length(params$General)==1L && (is.na(params$General) | params$General=="NA")
  if (testing) {
    fnc_get_local_file <- function(x=NULL) {
      pkg_path <- system.file(package = "ecerto")
      file_path <- list.files(path=pkg_path, pattern = x, recursive = TRUE)[1]
      return(file.path(pkg_path, file_path, fsep="/"))
    }
    tmp <- new.env()
    load(file = fnc_get_local_file(x="CRM001.RData"), envir = tmp)
    res <- get(x = "res", envir = tmp)
    G <- res$General
    C <- res$Certification
    CP <- res$Certification_processing
    #CP$CertValPlot
    A <- ifelse(!is.null(res$selected_tab), res$selected_tab, names(G$apm)[1])
    D <- G$apm[[A]]
    L <- fnc_get_local_file(x="BAMLogo2015.png")
  } else {
    G <- params$General
    C <- params$Certification
    CP <- params$Certification_processing
    A <- ifelse(params$selected_tab %in% names(G$apm), params$selected_tab, names(G$apm)[1])
    D <- G$apm[[A]]
    #L <- ifelse(exists(params[["logo_file"]]), params[["logo_file"]], NA)
    L <- params[["logo_file"]]
  }
```

```{r Logo, echo=FALSE, out.width="20%", fig.align="right"}
  knitr::include_graphics(L)
```

## *eCerto* Analyte Report

### Meta Data

|               |                |              |                                     |
|--------------:|:---------------|-------------:|:------------------------------------|
| **Study ID:** | `r G$study_id` |    **Date:** | `r format(Sys.time(), '%d %B, %Y')` |
|     **User:** | `r G$user`     | **Analyte:** | `r A`                               |

### Data Import

These files have been provided to the tool by `r G$user`:

```{r data_files, echo=FALSE, comment=NA}
  cat(paste(C$input_files, collapse=",\n"))
```

This is the imported data which was basis for all further calculations:

```{r data_table, echo=FALSE}
  df <- C$data[C$data[,"analyte"]==A,1:7,drop=FALSE]
  if (knitr::is_html_output()) {
    kableExtra::kable_styling(knitr::kable(df, format="html", row.names=FALSE, format.args = list(decimal.mark = ".")), font_size = 9)
  } else if (knitr::is_latex_output()) {
    knitr::kable(df, row.names=FALSE, format="latex", format.args = list(decimal.mark = "."))
  } else {
    knitr::kable(df, row.names=FALSE, format="pipe", format.args = list(decimal.mark = "."))
  }
```

### Statistics regarding lab means, lab variances and outlier detection

```{r Outlier_Stats, echo=FALSE, comment=NA}
  df <- CP$stats
  if (knitr::is_html_output()) {
    kableExtra::kable_styling(knitr::kable(df, format="html", row.names=FALSE, format.args = list(decimal.mark = ".")), font_size = 9)
  } else if (knitr::is_latex_output()) {
    knitr::kable(df, row.names=FALSE, format="latex", format.args = list(decimal.mark = "."))
  } else {
    knitr::kable(df, row.names=FALSE, format="pipe", format.args = list(decimal.mark = "."))
  }
```

`r ifelse(!is.null(D$sample_filter), "The following samples (IDs) have been removed by the user upon inspection of the oulier statistics:", "")`

```{r S_flt, echo=FALSE, comment=NA}
cat(paste(D$sample_filter, collapse=", ")) 
```

### Statistics regarding overall mean distribution and variance testing

```{r lab_means, eval=TRUE, echo=FALSE, comment=NA}
df <- CP$mstats
  if (knitr::is_html_output()) {
    kableExtra::kable_styling(knitr::kable(df, format="html", row.names=FALSE, format.args = list(decimal.mark = ".")), font_size = 9)
  } else if (knitr::is_latex_output()) {
    knitr::kable(df, row.names=FALSE, format="latex", format.args = list(decimal.mark = "."))
  } else {
    knitr::kable(df, row.names=FALSE, format="pipe", format.args = list(decimal.mark = "."))
  }
```

`r ifelse(!is.null(D$lab_filter), "The following Labs (IDs) have been removed by the user upon inspection of the oulier statistics:", "")`

```{r L_flt, echo=FALSE, comment=NA}
cat(paste(D$lab_filter, collapse=", ")) 
```

### Certified Values Plot

```{r CertValPlot, eval=TRUE, echo=FALSE, comment=NA, fig.width=CP$CertValPlot$Fig01_width/72, fig.height=CP$CertValPlot$Fig01_height/72}
  CertValPlot <- eval(parse(text=CP$CertValPlot$fnc))
  data <- C$data[C$data[,"analyte"]==A,,drop=FALSE]
  data[,"L_flt"] <- data[,"Lab"] %in% D$lab_filter
  data <- data[!(data[,"ID"] %in% D$sample_filter),]
  eval(CP$CertValPlot$call)
```

### Certified Value and uncertainty contributions

Here we could include the Tab.3 from the App including the certified values. However, this might be better done in the Material Report/Certificate.

---

***Note!*** This is a Report template for demonstration purpose. Specific layouts can be generated on demand.
