### Details on tests

Tests used for outlier detection often rely on tabulated critical values. Decisions 
to reject or not reject a potential outlier can be dependent on the source of the 
critical values.

Where ever possible, we tried to omit using fixed tables and rather implemented 
critical value calculation *ab initio*. However, to be transparent, we detail the 
mathematical approach for each test in the following.

***Note!*** Several test functions were implemented based on the functions in 
the R package `outliers` by Lukasz Komsta. Modifications were made to allow testing
up to n=100 laboratories (was restricted to n=30 in package `outliers`).

#### Cochran

The critical value is calculated internally using formula

```{r}
eCerto:::qcochran
```
where *p*, *n* and *k* are the desired p-value level, the number of replicates 
per group and the number of groups respectively. `stats::qf()` is the quantile 
function of the f-distribution as implemented in the R `stats` package. Likewise, 
`stats::pf()` is used to compute the Cochran P-value via

```{r}
eCerto:::pcochran
```

The test is based on "Snedecor, G.W., Cochran, W.G. (1980). Statistical Methods 
(seventh edition). Iowa State University Press, Ames, Iowa".

#### Dixon

The Dixon test statistic is calculated depending on the number of labs (n) using

```{r}
eCerto:::dixon.test
```

In ***eCerto*** the one-sided version of the Dixon test is applied consecutively
at the lower and upper end. Critical values are stored in tabulated form internally 
and have been combined in a single table from 
[this source](http://www.statistics4u.com/fundstat_eng/cc_outlier_tests_dixon.html).

```{r}
eCerto::cvals_Dixon[,1:8]
```

Values for non-tabulated combinations of *p* and *n* are derived by interpolation
using function `qtable`

```{r}
eCerto:::qtable
```

The test is based on:  
"Dixon, W.J. (1950). Analysis of extreme values. Ann. Math. Stat. 21, 4, 488-506"  
"Dean, R.B.; Dixon, W.J. (1951). Simplified statistics for small numbers of observations. Anal.Chem. 23, 636-638"  
"Dixon, W.J. (1953). Processing data for outliers. J. Biometrics. 9, 74-89"

#### Grubbs

The Grubbs test statistic is calculated either for a single or a double outlier at
both ends of the distribution consecutively using

```{r}
eCerto:::grubbs.test
```

Critical values for the single Grubbs test are calculated internally using

```{r}
eCerto:::qgrubbs
```

Critical values for the double Grubbs test are stored in tabulated form internally 
and P-values are derived by comparison.

```{r}
eCerto::cvals_Grubbs2[,1:4]
```

***Note!*** Critical values for double Grubbs are obtained from the `outliers` package 
for 4≤n≤30 and are estimated for 31≤n≤100 based on the approximation described in
[this paper](https://link.springer.com/article/10.1007/s10182-011-0185-y).

The test is based on:  
"Grubbs, F.E. (1950). Sample Criteria for testing outlying observations. Ann. Math. Stat. 21, 1, 27-58".

#### Scheffe

The Scheffe multiple comparison test is a re-implementation of the function `scheffe.test()`
as published in the `agricolae` package. It is calculated on the result of `stats::lm()`.

```{r}
eCerto:::scheffe.test
```

The test is based on:  
"Steel, R.; Torri, J.; Dickey, D. (1997) Principles and Procedures of Statistics: A Biometrical Approach. pp189"
