### Statistics on the distribution of lab means

The distribution of lab means is evaluated using a variety of recommended tests. 
Normality of the distribution is tested using the KS-Test. Besides `mean` and `sd` 
the robust alternatives `median` and `MAD`are provided. Columns of the form *testname~p~*
provide P-values of the respective tests. Skewness and Kurtosis are computed 
additionally and grouped with their respective tests (Agostino and Anscombe).

```{r TabC2, echo=FALSE, message=FALSE, results='asis'}
x <- eCerto::CRM001$Certification$data
eCerto:::styleTabC2(eCerto:::prepTabC2(dat = x[x[,"analyte"]=="Z",]), output="ft")
```

To compute the statistical tests *eCerto* uses functions from different packages 
available for **R**. Details regarding the conducted statistical test can be found 
using the following links:

```{r, echo=FALSE, message=FALSE}
sl <- eCerto::save_link
```

* `r sl("Bartlett", "https://rdrr.io/r/stats/bartlett.test.html")`s-test of the 
null hypothesis that the variances in each of the labs is the same.
* `r sl("ANOVA", "https://rdrr.io/r/stats/anova.html")` tests if labs are 
significantly different from each other (which is almost always the case).
***Note!*** It is ok to select the `pooling` option (Tab.C3) for this analyte if 
the ANOVA P-value be not significant.
* `r sl("KS", "https://rdrr.io/r/stats/ks.test.html")`-test performs a one-sample 
(Kolmogorov) test, which is carried out of the null that the distribution of lab 
means is similar to a normal distribution with parameters $\mu$ and $\sigma$ 
estimated from the analyte data.
* `r sl("Skewness", "https://rdrr.io/cran/moments/man/skewness.html")` computes 
the skewness of the distribution.
* `r sl("Agostino", "https://rdrr.io/cran/moments/man/agostino.test.html")`
performs the D'Agostino test for skewness in normally distributed data.
***Note!*** Some tests (*i.e.* Agostino) need a minimum number of replicates and 
will not yield a result if this criteria is not met.
* `r sl("Kurtosis", "https://rdrr.io/cran/moments/man/kurtosis.html")` computes 
the estimator of Pearson's measure of kurtosis.
* `r sl("Anscombe", "https://rdrr.io/cran/moments/man/anscombe.test.html")` performs 
the Anscombe-Glynn test of kurtosis for normal distributed samples.
***Note!*** `Skewness` and `Kurtosis` are computed using a two-sided alternative.

Additionally to checking the `KS` test P-value, deviation of the data from a 
normal distribution can also be visually investigated by opening a QQ-plot using 
the respective link.
