### Stability linear model plot (

#### Standard version

The uncertainty contribution of the stability measurements `u_stab` is calculated 
for each analyte based on a linear model of `Value` on `Date`, or, more precisely, 
on the monthly difference `mon_diff` calculated based on the imported `Date` 
values.

The data and linear model is visualized in **Fig.S1**. Here, in addition to the 
monthly difference plotted on the bottom axis, start and end date of the data 
points are depicted at the top of the plot.
The red line indicates the certified value $\mu_c$ and the two green dashed lines 
provide either the standard deviation $2s$ of the data or $U_{abs}$ from the 
table of certified values, based on availability and user choice.

```{r FigS1, echo=FALSE, message=FALSE, fig.cap="**Fig.S1** Linear model plot visualizing stability data", out.width="100%"}
x <- eCerto::LTS001[[1]]
x$def$KW <- NA
eCerto:::plot_lts_data(x = x, type = 1, t_cert = 160, show_legend = TRUE)
```

***Note!*** If no table of certified values is present or the analyte is yet 
unconfirmed, than red and green lines represent mean and standard deviation of 
the currently depicted stability data.

The dashed blue line indicates the linear model. It's parameter $b_1$ is reported 
in **Tab.S1** and used to calculate `u_stab` via its Std. Error $s(b_1)$ multiplied
by the shelf life $t_{cert}$.

#### Adjusted version

Alternatively, an adjusted version of the plot can be drawn. Adjusted means that
the measured values are corrected by the differences between their mean and the
value of $\mu_c$. Let us assume that certified values are present in **Tab.C3** 
and provided to the Figure drawing function. In this case $\mu_c$ and $U_{abs}$ 
are depicted together with $U_{abs}/3$.

```{r FigS1_adjusted, echo=FALSE, message=FALSE, fig.cap="**Fig.S1_adj** Linear model plot visualizing stability data", out.width="100%"}
x[["def"]][["U_Def"]] <- "U"
eCerto:::plot_lts_data(x = x, type = 3, t_cert = 60, show_legend = TRUE)
```

Labels for constant values are depicted on the left side of the figure. On the 
right side, $u_{LTS}$ is annotating the values calculated by $t_{cert}*SE(b_1)$.
Similarly, $u_{CRM}$ is annotating the potential values of $U_{abs}$ given that
a specific $u_{LTS}$, depending on the selection of $t_{cert}$, is incorporated
in **tab.C3**, thereby expanding the uncertainty. Because the value of $u_{LTS}$
is incorporated in its quadratic form, $u_{CRM}$ is a curve.

In contrast to the standard version of the stability plot, the confidence 
interval of the linear model slope $CI_{95}(b_1)$ is shown.
