## Method validation

***Note!***
The Validation module is an add-on to *eCerto*. It is not required to compute CRM
statistics. It is ment to:

- quickly validate working area and linearity of a newly developed analytical 
method (according to DIN 32645) or to
- validate an analytical method based on data from a collaborative trial 
according to (DIN 5725-2). 

As it is currently work-in-progress, available options and output format might 
change in the future.

## DIN 32645

```{r child = 'v_datapreparation.Rmd'}
```

```{r child = 'v_dataupload.Rmd'}
```

```{r child = 'v_fig_V1.Rmd'}
```

```{r child = 'v_tab_V1.Rmd'}
```

```{r child = 'v_trueness.Rmd'}
```

```{r child = 'v_precision.Rmd'}
```

```{r child = 'v_uncertainty.Rmd'}
```

```{r child = 'v_formula_collection.Rmd'}
```

### Validation report and data backup

The user can export a report, in HTML or docx format, containing all imported, 
edited and calculated data and figures.

For later reference, all data and parameters can be stored (and reimported) in an
RData file.

## DIN 5725-2

```{r child = 'v2_dataupload.Rmd'}
```

Functions and output have been tested using the example data B1, B2 and B3 from 
DIN 5725-2 and confirmed to be in accordance with the presented results.

Further documentation t.b.d..

<br/>
<br/>
